Verifying Demonstrations

### 2021-06-17 paper/sybil-free-pseudonyms.tex
Removes redundant anon-cred text
Puts \input for anon-creds.tex in a better place
Cuts in Sybil-free pseudonyms/anon cred
Changes to use the same ref to Leonardo's work

We must protect against Sybil attacks~\cite{SybilAttack}.
We use the idea of identity domains and self-certified Sybil-free pseudonyms 
proposed by \textcite{SelfCertifiedSybilFreePseudonyms}.
However, we don't need the ability to (nor want to be able to) deanonymize 
pseudonyms, so we don't use the entire e-token dispenser scheme by 
\textcite{HowToWinTheCloneWars} that 
\textcite{SelfCertifiedSybilFreePseudonyms} use, but rather just what they call 
the token serial number.

>>>>

We must protect against Sybil attacks~\cite{SybilAttack}.
We use the idea of identity domains and self-certified Sybil-free pseudonyms 
proposed by \textcite{SybilFreePseudonyms}.
However, we don't need the ability to (nor want to be able to) deanonymize 
pseudonyms, so we don't use the entire e-token dispenser scheme by 
\textcite{HowToWinTheCloneWars} that 
\textcite{SybilFreePseudonyms} use, but rather just what they call 
the token serial number.
More specifically, what we need is an anonymous credential system with the 
following properties.

\input{anon-cred.tex}
